IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-05-11 paper/appendix.tex
More on extention formalism.

\begin{figure}
  %{
  %format .->  = "\overset{\alpha}{\hookrightarrow}"
  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
  \begin{code}
    iv  ::= cdots | Labeled il ie
    ie  ::= cdots | label ie ie | unlabel ie | labelOf ie
    iE  ::= cdots | label iE ie | unlabel iE | labelOf iE
  \end{code}

  \begin{mathpar}
    \inferrule[I-label]
    {|
      il canFlowTo il'
    |}
    {|
      niconf iS id il (label il' ie)
      ->
      niconf iS id il (Labeled il' ie)
    |}
    \and
    \inferrule[I-unlabel]
    {|
      il''=il lub il'
    |}
    {|
      niconf iS id il (unlabel (Labeled il' ie))
      ->
      niconf iS id (il'') ie
    |}
    \and
    \inferrule[I-labelOf]
    {|
    |}
    {|
      niconf iS id il (labelOf (Labeled il' ie))
      ->
      niconf iS id il (il')
    |}
  \end{mathpar}
  \caption{}
  \label{fig:labeled-vals}
  %}
\end{figure}

@@

  \begin{mathpar}
    \inferrule[I-new]
    {
      |il canFlowTo il'| \\
      |fresh ia|
    }
    {|
      niconf iS id il (new il' iv)
      ->
      niconf iS id il (iall il')
      |}
    \and
    \inferrule[I-read]
    {|
      il canFlowTo il'
      |}
    {|
      niconf iS id il (label il' ie)
      ->
      niconf iS id il (Labeled il' ie)
      |}
    \and
    \inferrule[I-write]
    {|
      il canFlowTo il'
      |}
    {|
      niconf iS id il (label il' ie)
      ->
      niconf iS id il (Labeled il' ie)
      |}
    \and
    \inferrule[I-labelOf2]
    {|
      il canFlowTo il'
      |}
    {|
      niconf iS id il (label il' ie)
      ->
      niconf iS id il (Labeled il' ie)
      |}
  \end{mathpar}
  \caption{}
  \label{fig:labeled-refs}
  %}
\end{figure}

>>>>

\begin{figure}
  %{
  %format .->  = "\overset{\alpha}{\hookrightarrow}"
  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
  \begin{code}
    iv  ::= cdots | Labeled il ie
    ie  ::= cdots | label ie ie | unlabel ie | labelOf ie
    iE  ::= cdots | label iE ie | unlabel iE | labelOf iE
  \end{code}
  \begin{mathpar}
    \inferrule[I-label]
    {|
      il canFlowTo il'
    |}
    {|
      niconf iS id il (label il' ie)
      ->
      niconf iS id il (Labeled il' ie)
    |}
    \and
    \inferrule[I-unlabel]
    {|
      il''=il lub il'
    |}
    {|
      niconf iS id il (unlabel (Labeled il' ie))
      ->
      niconf iS id (il'') ie
    |}
    \and
    \inferrule[I-labelOf]
    {|
    |}
    {|
      niconf iS id il (labelOf (Labeled il' ie))
      ->
      niconf iS id il (il')
    |}
  \end{mathpar}
  \caption{}
  \label{fig:labeled-vals}
  %}
\end{figure}

@@

  \begin{mathpar}
    \inferrule[I-new]
    {
      |il canFlowTo il'| \\
      |fresh ia|\\
      |iS'= bracket iS (mapsto (iall il') iv)|
    }
    {|
      niconf iS id il (new il' iv)
      ->
      niconf iS' id il (iall il')
      |}
    \and
    \inferrule[I-read]
    {}
    {|
      niconf iS id il (read ial')
      ->
      niconf iS id (il lub il') (readState iS (iall il'))
      |}
    \and
    \inferrule[I-write]
    {
      |il canFlowTo il'|\\
      |iS'= bracket iS (mapsto (iall il') iv)|
    }
    {|
      niconf iS id il (write ial' iv)
      ->
      niconf iS' id il (unit)
      |}
    \and
    \inferrule[I-labelOf2]
    {}
    {|
      niconf iS id il (labelOf ial')
      ->
      niconf iS id il (il')
      |}
  \end{mathpar}
  \caption{}
  \label{fig:labeled-refs}
  %}
\end{figure}

\begin{figure}
  \begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
  &|fullconf id il' tS ie| \begin{cases}
  |bullet| & |il' cantFlowTo il| \\
  |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
  \end{cases} \\
  &|erase il emptyset = emptyset|\\
  &|erase il (bracket iS (mapsto id Q)) =| \begin{cases}
  |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
  & \text{the label of thread |id|} \\
  |bracket (erase il iS) (mapsto id (erase il Q))| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|\\
  &|erase il v = v|
  \end{align*}
  \caption{Erasure function for the full IFC language, with all extensions.
    In all not specified (including target-language constructs),
    |erasef il| is applied homomorphically.}
  \label{fig:erasure2}
\end{figure}
